Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-03-13 paper/main.tex
minor changes

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ & 
filament &none & $<10^{12}$\hMsun\\

&   & & 
filament & - & $>10^{12}$\hMsun\\

&   & & 
wall & none & $<10^{12}$\hMsun\\

&   & & 
wall & none & $>10^{12}$\hMsun\\\hline

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ & 
filament &none & $<10^{12}$\hMsun\\

&   & & 
filament & none & $>10^{12}$\hMsun\\

&   & & 
wall & none & $<10^{12}$\hMsun\\

&   & & 
wall & + & $>10^{12}$\hMsun\\\hline

@@

& & &
wall& $+$ & $<10^{12}$\hMsun\\
& &    &
wall & $++$ & $>10^{12}$\hMsun\\\hline \hline

\end{tabular}
\caption{Spin alignment with the cosmic web. Summary of theoretical
  results provided by methods similar to ours.}

@@

The spin is calculated as
\begin{equation}
\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
\end{equation}
where the velocities are also measured with respect to the center of
mass velocity. Finally the peculiar velocity of a halo is computed as
the center of mass velocity.

The halo data used in this paper is publicly available through the
MultiDark
database\footnote{\texttt{http://www.multidark.org/MultiDark/}} and is
thoroughly described in \cite{2013AN....334..691R}.

@@

CAMBIE EL ORDEN DE PARRAFOS PARA QUE LA FIGURA SE LEA DE IZQ A DERECHA:

>>>>

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ & 
filament & - & $>10^{12}$\hMsun\\

&   & & 
filament & none & $<10^{12}$\hMsun\\

&   & & 
wall & none & $>10^{12}$\hMsun\\

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ & 
filament &none & $>10^{12}$\hMsun\\

&   & & 
filament & none & $<10^{12}$\hMsun\\

&   & & 
wall & + & $>10^{12}$\hMsun\\

&   & & 
wall & nonte & $<10^{12}$\hMsun\\\hline

@@

& & &
wall & $++$ & $>10^{12}$\hMsun\\
& &    &
wall& $+$ & $<10^{12}$\hMsun\\\hline \hline

\end{tabular}
\caption{Angular momentum alignment with the cosmic web. Summary of theoretical
  results provided by methods similar to ours.}

@@

The angular momentum is calculated as
\begin{equation}
\vec{J} = \sum_{i}m_p{R_i}\vec{v}_i, 
\end{equation}
where the velocities are also measured with respect to the center of
mass velocity. Finally the peculiar velocity of a halo is computed as
the center of mass velocity.

The halo and environment used in this paper is publicly available through the
MultiDark
database\footnote{\texttt{http://www.multidark.org/MultiDark/}}. The
halo data is thoroughly described in \cite{2013AN....334..691R}.

@@
